Missing data: Current practice in football research and recommendations for improvement

### 2020-09-04 paper/paper.Rmd
change wording in the search.

For clarity, we describe an example of missingness. An Australian Rules Football data collector 
was taking lunch during the third quarter, so no data was recorded for this time period. This
would be considered missing data. Compare this to the game being cancelled due to a pandemic. 
There is no missing data because there is no data to be observed. Similiarly, if a study screens out individuals who 
do not meet inclusion criteria, this is not a missing value, because there is no intent for these 
values to be observed or measured.

Data does not go missing the same way every time. There are three broad
categorisations describing why data can be missing: Missing Completely
at Random (MCAR), Missing at Random (MAR), and Missing Not at Random
(MNAR). These categorisations help describe whether the missingness
occurs by chance (MCAR), due to some observed variable (MAR) or an
unobserved variable (MNAR), with MCAR being the least harmful, and MAR and MNAR
biased [@Newman2014]. Football relevant examples are provided in Supplement X, and
more detailed explanations of MCAR, MAR, MNAR can be found elsewhere
[@Sainani2015; @Nakagawa2008; Sterne2009].

@@

It is imperative that missing data, or lack thereof, are reported [@Schafer2002]. 
While there has been significant interest in modelling missing
data [@refs], the exploration and reporting of missings have received
less attention [@Schafer2002]. This article aimed to: (1) estimate the proportion
of articles that report missing data in football research; (2) highlight
several improvable missing data practices; and (3) provide recommendations for
exploring and reporting missingness.

@@

Our intention was to survey, at random, 10% of the total articles found
(after title and abstract screening). We were primarily interested in
whether missing data were reported or acknowledged; and if not, whether
a dataset was shared. Where applicable, information about how missing
values were handled was also extracted (see Supplement 2). Two authors
independently extracted the data (X% agreement). Findings are reported
as the proportion and 95% confidence interval. Supplement 2 provides
further details of the search.

>>>>

For clarity, we describe an example of missingness. An Australian Football data collector 
was taking lunch during the third quarter, so no data was recorded for this time period. This
would be considered missing data. Compare this to the game being cancelled due to a pandemic. 
There is no missing data because there is no data to be observed. Similiarly, if a study screens out individuals who do not meet inclusion criteria, this is not a missing value, because there is no intent for these values to be observed or measured.

Data does not go missing the same way every time. There are three broad
categorisations describing why data can be missing: Missing Completely
at Random (MCAR), Missing at Random (MAR), and Missing Not at Random
(MNAR). These categorisations help describe whether the missingness
occurs by chance (MCAR), due to some observed variable (MAR) or an
unobserved variable (MNAR), with MCAR being the least harmful, and MAR and MNAR
biased [@Newman2014]. Football relevant examples are provided in Supplement 1, and
more detailed explanations of MCAR, MAR, MNAR can be found elsewhere
[@Sainani2015; @Nakagawa2008; Sterne2009].

@@

It is imperative that missing data, or lack thereof, are reported [@Schafer2002]. 
While there has been significant interest in modelling missing
data [@refs], the exploration and reporting of missings have received
less attention [@Schafer2002]. This article aimed to: (1) estimate the proportion
of articles that report missing data in football research; (2) highlight
several practices that should be avoided; and (3) provide recommendations for
exploring and reporting missingness.

@@

Our intention was to survey, at random, 10% of the total articles found, after 
title and abstract screening. We were primarily interested in
whether missing data was reported or acknowledged; and if not, whether
a dataset was shared. Where applicable, information relating to how missing
values were treated was also extracted (Supplement 2). Two authors
independently extracted the data (X% agreement). Findings are reported
as the proportion and 95% confidence interval. 
Further details of the search can be found in Supplement 2.
